---
title: "Ume책 Software Carpentry Workshop Invoice"
author: "Alistair Bailey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    includes:
      in_header: mysty.sty
      fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE,echo=FALSE, message=FALSE, 
                      warning=FALSE, fig=TRUE,eval=TRUE)
#library(pander)
library(tidyverse)

# Exchange rate 12th October 2018
nok_gbp <- 10.82
nok_sk <- 0.91
gbp_nok <- 0.093
```

## Invoice for Software Carpentry Instruction Ume책 9-10th October 2018

The workshop was hosted by High Performance Computing Center North (HPC2N) at
Ume책 University SE-901 87, Ume책, Sweden in affiliation with the Nordic eInfrastructure Collaboration. 

### Exchange rate

Exchange rates on the 12th October 2018: 

- 1 GBP = 10.82 NOK
- 1 SEK = 0.91 NOK
- 1 NOK = 0.093 GBP

### Table of expsenses

Please see attached receipts
 
```{r expenses}
parking <- 63.30 * nok_gbp
hotel_uk <- 42 * nok_gbp
flights <- 320.5 * nok_gbp
hotel_um <- 301.45 * nok_gbp
bus <- 100 * nok_sk

tot_exp <- sum(parking,hotel_uk,hotel_um,flights,bus)

total_gbp <- tot_exp * gbp_nok

exp_table <- tibble(Expense = c("Heathrow Airport Parking", 
                                "Heathrow Airport Hotel",
                                "Flights",
                                "Umea Airport Bus",
                                "Umea Hotel"),
                    'Cost GBP/SEK' = c(63.30,
                                       42,
                                       320.5,
                                       100,
                                       301.45),
                    'Cost NOK' = c(parking,
                                   hotel_uk,
                                   flights,
                                   bus,
                                   hotel_um))
pander::pander(exp_table,justify = c('left', 'center', 'center'))
```

Total costs **`r format(sum(exp_table[,3]))` NOK**

Total costs `r format(sum(exp_table[,3])*gbp_nok)` GBP

### Payment information

Please make payment to:

- Account name: Mr A Bailey
- Account holder address: Flat 17, 115 Regents Park Road, Southampton, SO15 8AH, United Kingdom
- Bank Identifier Code (BIC): NAIAGB21
- SWIFT Intermediary Bank address: MIDLGB22
- International Bank Account Number (IBAN): GB12 NAIA 0702 4646 2570 33
